|

### 2017-10-07 manuscript.Rmd
paras merged

Docker permits convenient access to pre-configured and create
_binary_ images that "just work."  This allows R users to access a
wider-variety of ready-to-use environments than the R Project
itself provides.  For example, R users on Windows may run RStudio
Server or Shiny Server locally just by launching a single command
(once Docker itself is installed), access R-devel without affecting
their local system and more.  Here, we detail the some of the principle
use cases motivate these containerized versions of R environments
and the design principles that help make them work.

>>>>

Docker gives users very convenient access to pre-configured and
pre-built _binary_ images that "just work".  This allows R users to
access a wider-variety of ready-to-use environments than provided by
either the R Project itself or, say, their distribution which will
generally focus on one (current) release.  For example, R users on
Windows may run RStudio Server or Shiny Server locally just by launching
a single command (once Docker itself is installed). Another common
use-case is access to R-devel without affecting the local system and
more. Here, we detail the some of the principle use cases motivate these
containerized versions of R environments and the design principles that
help make them work.
